Ornaments as indicators of social changes and cultural practices in northeast Taiwan before and after European colonial period

### 2019-12-08 analysis/paper/paper.Rmd

```{r C14-table-data}
kw_dates <- readxl::read_excel(here("analysis", "data", "raw_data", "KWL_C14_dates.xlsx"))
table_kw_dates <-
  kw_dates %>% 
  mutate(`Depth related to sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  mutate(Period = as.factor(Period)) %>% 
  mutate(Period = factor(Period,
                       level = c("pre-European", 
                                 "European", 
                                 "post-European"))) %>% 
  arrange(Period) %>% 
  select("Pit-Layer", "Depth related to sea level (cm)", Period, "Date BP", "Calibrated date", "Details")

knitr::kable(table_kw_dates,
             caption = "Radiocarbon dates on charcoals from Kiwulan")
```

```{r C14-data, fig.cap= "Summed probability distributions for dates from Kiwulan. The y-axis represents summed probability and the x-axis is the date in calendar years. Produced with the BChronDensity() function in program R's Bchron package (Parnell et al. 2008). IntCal13 Atmospheric curve."}

@@

>>>>

```{r C14-table-data}
kw_dates <- readxl::read_excel(here("analysis", "data", "raw_data", "KWL_C14_dates.xlsx"))
cal_kw_dates <- readr::read_csv(here("analysis", "data", "raw_data", "kwl_cal_dates.csv"))

table_kw_dates <-
  kw_dates %>% 
  mutate(`Depth related to sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  mutate(Period = as.factor(Period)) %>% 
  mutate(Period = factor(Period,
                       level = c("pre-European", 
                                 "European", 
                                 "post-European"))) %>% 
  arrange(Period) %>% 
  left_join(cal_kw_dates, "Pit-Layer") %>% 
  select("Period", "Pit-Layer", "Depth related to sea level (cm)", "Date BP", "Calibrated date (95% conf. level)", "Details")

knitr::kable(table_kw_dates,
             caption = "Radiocarbon dates on charcoals from Kiwulan (Chen 2007). Recalibrated using IntCal13 Atmospheric curve.")
```

```{r C14-data, fig.cap= "Summed probability distributions for dates from Kiwulan. The y-axis represents summed probability and the x-axis is the date in calendar years. Produced with the BChronDensity() function in program R's Bchron package (Parnell et al. 2008)."}

@@

# get and summarise the 95% credible interval for each sample into a dataframe
kw_age_samples <- sampleAges(kw_dates_with_error_calibrated)
kw_age_cali_df <- as.data.frame(t(apply(kw_age_samples, 2, 
                                        quantile, prob=c(0.025,0.975))))

# tidy the dataframe 
kw_age_cali_df_tidy <-
  kw_age_cali_df %>% 
  rownames_to_column(var = "Pit-Layer") %>% 
  mutate(`Calibrated date (95% conf. level)`= paste0(`2.5%`," - ", `97.5%`))

# save the dataframe
write.csv(kw_age_cali_df_tidy, here("analysis/data/raw_data/kwl_cal_dates.csv"))
